Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-05-05 paper/paper.tex
Fix some figure styling
Renamed rendered pdf files

\begin{figure*}[t]
\includegraphics[width=0.98\textwidth]{figures-mini-2x2-secure-response-redirect-ybar.pdf}
\caption{Secure connections for succesful connections when trying to use HTTPS.
(Note that the majority of websites (as per Figure~\ref{fig:httpsDiff}) do not respond.)}
\label{fig:https}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
\includegraphics[width=0.31\textwidth]{figures-mini-1x1-internal-resources-cdf.pdf}
\caption{External third-party resource usage.}
\label{fig:external}
\vspace{-0pt}
\end{figure}

@@

%%INSERT FIGURES (a) and (b) FROM THIS MORNINGS FIGURES ...
\begin{figure*}[t]
\includegraphics[width=0.98\textwidth]{figures-mini-2x2-categories-organizations-ybar.pdf}
\caption{Domain covererage of different categories of known tracker services (top row)
and companies (bottom row), as per Disconnect's blocking list.}
\label{fig:categories-companies}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures-mini-2x1-categories-scatter.pdf}
\begin{tabular}{cc}
(a) Sweden &
(b) Global \\
\end{tabular}
\caption{Correlation of tracker coverage seen with HTTP and HTTPS.}
\label{fig:scatter}
\vspace{-0pt}
\end{figure}

>>>>

\begin{figure*}[t]
(Figure removes; it's the same as the next figure with both HTTPS and HTTP rows.)
\caption{Secure connections for succesful connections when trying to use HTTPS.
(Note that the majority of websites (as per Figure~\ref{fig:httpsDiff}) do not respond.)}
\label{fig:https}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
\includegraphics[width=0.47\textwidth]{figures-mini-1x1-internal-resources-cdf.pdf}
\caption{External third-party resource usage.}
\label{fig:external}
\vspace{-0pt}
\end{figure}

@@

%%INSERT FIGURES (a) and (b) FROM THIS MORNINGS FIGURES ...
\begin{figure*}[t]
\includegraphics[width=0.98\textwidth]{figures-mini-2x2-categories-organizations-http-ybar.pdf}
\caption{Domain covererage of different categories of known tracker services (top row)
and companies (bottom row), as per Disconnect's blocking list.}
\label{fig:categories-companies}
\vspace{-0pt}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures-ng-mini-2x1-categories-scatter.pdf}
\begin{tabular}{cc}
(a) Sweden &
(b) Global \\
\end{tabular}
\caption{Correlation of tracker coverage seen with HTTP and HTTPS.}
\label{fig:scatter}
\vspace{-0pt}
\end{figure}
